### 2016-05-11 text/Chapter09.tex
Add binding to chapter 2, whitespace, tweaks

~ The second category of context-aware systems discussed in Section~\ref{sec:applications-structural}
captures \emph{per-variable} contextual properties. The systems discussed here resemble sub-structural
logics, but rather than \emph{restricting} variable use, they \emph{track} how the variables are used.

@@

Most of the further work has been discussed throughout the thesis, so this section
serves mainly as an overview. We follow the same structure as when discussing pathways to 
coeffects (Chapter~\ref{ch:pathways}). We consider further work related to syntactic approach
to coeffect systems, categorical semantics of coeffects, and connections with sub-structural type 
systems and bunched logics.

>>>>

~ The second category of context-aware systems discussed in Section~\ref{sec:applications-structural}
captures \emph{per-variable} contextual properties. The systems discussed here resemble substructural
logics, but rather than \emph{restricting} variable use, they \emph{track} how the variables are used.

@@

Most of the further work has been discussed throughout the thesis, so this section
serves mainly as an overview. We follow the same structure as when discussing pathways to
coeffects (Chapter~\ref{ch:pathways}). We consider further work related to syntactic approach
to coeffect systems, categorical semantics of coeffects, and connections with substructural type
systems and bunched logics.
